---
title: "Notebook with the HW from Statistical Rethinking, 2023 edition"
date: "Spring 2023"
output: 
    html_document:
     df_print: paged
     toc: true
     toc_float: true
---

```{r, setup-options, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, out.width = "100%", fig.align = "center"
)
```

```{r}
library(rethinking)
```

# __Week 1 Problems__

## Problem 1

Suppose the globe tossing data has turned out to be 4 water and 11 land. Construct the posterior distribution[^1].

```{r}
#Function to compute posterior distribution

compute_posterior <- function(the_sample, poss=c(0, 0.25, 0.5, 0.75, 1)) {
  W <- sum(the_sample == "W")
  L <- sum(the_sample == "L")
  ways <- sapply(poss, function(x) x^W * (1-x)^L)
  post <- ways/sum(ways)
  data.frame(poss, ways, post = round(post, 3))
}

#Our sample

samp <- c(rep("W", 4), rep("L", 11))
compute_posterior(samp, poss=seq(from=0, to=1, len=11))
```

## Problem 2

Using the posterior distribution from 1, compute the posterior predictive distribution for the next 5 tosses of the same globe. Using the sampling method is recommended. 

```{r}
p_samples <- rbeta(1e4, 4+1, 11+1)
W_sim <- rbinom(1e4, size=5, p=p_samples)
plot(table(W_sim), ylab="Count", xlab="Number of W")
```

## Problem 3

Use the posterior predictive distribution from 2 to calculate the probability of >= 3 water samples in the next 5 tosses. 

```{r}
sum(W_sim >= 3)
```


[^1]: Unique combination of data, likelihood, parameters and priors leads to a unique _posterior distribution_. The distribution contains the relative plausibility of different parameter values, conditional on the data and model. 


